Printer ballistics through texture analysis of characters

### 2013-11-29 Printer_Ballistics.tex
Artigo finalizado de novo

\begin{table*}
\caption{Printers used in this work}
\label{tab:printers}
\begin{center}
    \begin{tabular}{ | c | c | c | c |}
    \hline
Printer & Documents & Characters ''e'' & Characters ''t'' \\ \hline
Brother-HL4070CDW & 28 & 252 & 252\\
Canon-D1150 & 28 & 252 & 252\\
Canon-MF3240 & 28 & 252 & 252\\
Canon-MF4370DN & 27 & 252 & 252 \\
HP-CLJ-CP2025A & 28 & 250 & 250\\
Lexmark-E260D & 30 & 636 & 629\\
\hline
    \end{tabular}
\end{center}    
\end{table*}

@@

Although not the purpose of this study, and future studies, manual extraction of characters is still a counterproductive way of working. Develop a (semi) automated method would be of great benefit to researchers in this field.

>>>>

\begin{table*}
\caption{Printers used in this work}
\label{tab:printers}
\begin{center}
    \begin{tabular}{ | c | c | c | c |}
    \hline
Printer & Documents & Characters ''e'' & Characters ''t'' \\ \hline
Brother-HL4070CDW & 28 & 252 & 252\\
Canon-D1150 & 28 & 252 & 252\\
Canon-MF3240 & 28 & 252 & 252\\
Canon-MF4370DN & 27 & 252 & 252 \\
HP-CLJ-CP2025A & 28 & 252 & 252\\
Lexmark-E260D & 28 & 252 & 252\\
\hline
    \end{tabular}
\end{center}    
\end{table*}

@@

Although not the purpose of this study, and future studies, manual extraction of characters is still a counterproductive way of working. Develop a (semi) automated method to do this would be of great benefit to researchers in this field.
